---
output:
  html_document:
    keep_md: yes
    toc: no
    self_contained: no
  pdf_document:
    toc: yes
---

# rStrava

##### *Marcus W. Beck, mbafs2012@gmail.com, Pedro Villarroel, pedrodvf@gmail.com*

### Overview and Installation

This is the development repository for rStrava, an R package to access data from the Strava API.  The package can be installed and loaded as follows:

```{r eval = F}
install.packages('devtools')
devtools::install_github('fawda123/rStrava')
```

### Issues and suggestions

Please report any issues and suggestions on the [issues link](https://github.com/fawda123/rStrava/issues) for the repository.

Linux: [![Travis-CI Build Status](https://travis-ci.org/fawda123/rStrava.svg?branch=master)](https://travis-ci.org/fawda123/rStrava)

Windows: [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/fawda123/rStrava?branch=master)](https://ci.appveyor.com/project/fawda123/rStrava)

### Package overview

The functions are in two categories depending on ease of use.  The first category of functions scrape data from the public Strava website and the second category uses the API functions.  The second category also requires an authentication token.  The help files for each category can be viewed using ```help.search```:

```{r eval = FALSE}
help.search('notoken', package = 'rStrava')
help.search('token', package = 'rStrava')
```


An example using the scraping functions:
```{r echo = FALSE, message = FALSE}
devtools::load_all('.')
```
```{r message = FALSE}
# get athlete data for these guys
athl_fun(c(2837007, 2527465), trace = FALSE)
```

More info forthcoming...

### License

This package is released in the public domain under the creative commons license [CC0](https://tldrlegal.com/license/creative-commons-cc0-1.0-universal). 
