---
output:
  html_document:
    keep_md: yes
    toc: no
    self_contained: no
  pdf_document:
    toc: yes
---

# rStrava

##### *Marcus W. Beck, mbafs2012@gmail.com, Pedro Villarroel, pedrodvf@gmail.com, Daniel Padfield, dp323@exeter.ac.uk*

### Overview and Installation

This is the development repository for rStrava, an R package to access data from the Strava API.  The package can be installed and loaded as follows:

```{r eval = F}
install.packages('devtools')
devtools::install_github('fawda123/rStrava')
```

### Issues and suggestions

Please report any issues and suggestions on the [issues link](https://github.com/fawda123/rStrava/issues) for the repository.

Linux: [![Travis-CI Build Status](https://travis-ci.org/fawda123/rStrava.svg?branch=master)](https://travis-ci.org/fawda123/rStrava)

Windows: [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/fawda123/rStrava?branch=master)](https://ci.appveyor.com/project/fawda123/rStrava)

### Package overview

The functions are in three categories depending on mode of use.  The first category of functions scrape data from the public Strava website and the second category uses the API functions or relies on data from the API functions.  The second category requires an authentication token.  The help files for each category can be viewed using ```help.search```:

```{r eval = F}
help.search('notoken', package = 'rStrava')
help.search('token', package = 'rStrava')
```

#### Scraping functions (no token)

An example using the scraping functions:
```{r echo = FALSE, message = FALSE}
devtools::load_all('.')
```
```{r message = FALSE}
# get athlete data for these guys
athl_fun(c(2837007, 2527465, 2140248), trace = FALSE)
```

#### API functions (token)

These functions require a Strava account and a personal API, both of which can be obtained on the Strava website.  The user account can be created by following instructions on the [Strava homepage](https://www.strava.com/).  After the account is created, a personal API can be created under API tab of [profile settings](https://www.strava.com/settings/api).  The user must have an application name (chosen by the user), client id (different from the athlete id), and an application secret to create the authentication token.  Additional information about the personal API can be found [here](https://strava.github.io/api/).  Every API retrieval function in the rStrava package requires an authentication token (called `stoken` in the help documents).  The following is a suggested workflow for using the API functions with rStrava.

First, create the authentication token using your personal information from your API.  Replace the `app_name`, `app_client_id`, and `app_secret` objects with the relevant info from your account.
```{r, eval = FALSE}

app_name <- 'myappname' # chosen by user
app_client_id  <- 'myid' # an integer, assigned by Strava
app_secret <- 'xxxxxxxx' # an alphanumeric secret, assigned by Strava

# create the authentication token
stoken <- httr::config(token = strava_oauth(app_name, app_client_id, app_secret))
```

The API retrieval functions can be used after the token is created.
```{r echo = FALSE}
source('extra.R')
```
```{r}
myinfo <- get_athlete(stoken, id = '2837007')
head(myinfo)
```

An example creating a heat map of activities:
```{r message = F, fig.height = 7, fig.width = 7, cache = TRUE}
library(dplyr)

# get activities, compile, filter by location
acts <- get_activity_list(stoken, '2837007') %>% 
	compile_activities %>% 
	filter(location_city %in% c('Pensacola', 'Pensacola Beach'))

get_heat_map(acts)
```


### License

This package is released in the public domain under the creative commons license [CC0](https://tldrlegal.com/license/creative-commons-cc0-1.0-universal). 